---
title: "Projet Machine Learning"
author: "Loïc"
date: "31/05/2020"
output: html_document
---

```{r setup, include=FALSE}
library(caret)
library(rpart)
library(rpart.plot)
library(randomForest)
library(corrplot)
library(Hmisc)
set.seed(19553)
knitr::opts_chunk$set(echo = TRUE)
```

## Import data :  

We import the data into tow dataframes, one for training set and the other for the testing set :   

```{r include=TRUE}
training<-read.csv("~/pml-training.csv",header=TRUE,sep=",",stringsAsFactors=FALSE)
testing<-read.csv("~/pml-testing.csv",header=TRUE,sep=",",stringsAsFactors=FALSE)
```

## Cleaning data :  
In order to clean the data we delete all columns with missing values.
And we keep only numerical columns and the variable we want predict (classe).  

```{r include=TRUE}

training<- training[, colSums(is.na(training)) == 0] 
testing<- testing[, colSums(is.na(testing)) == 0] 
trainDelete <- grepl("^X|timestamp|window", names(training))
training <- training[, !trainDelete]
classe <- training$classe
trainingCleaned <- training[, sapply(training, is.numeric)]
trainingCleaned$classe <- classe
testDelete <- grepl("^X|timestamp|window", names(testing))
testing <- testing[, !testDelete]
testingCleaned <- testing[, sapply(testing, is.numeric)]
```

## Slicing :  

we slice our data after cleaning into trainig data and testing data for validation. 75% of data will be in  the training set, the remained data goes for the testing set.  

```{r include=TRUE}
inTrain <- createDataPartition(trainingCleaned$classe, p=0.75, list=FALSE)
DataTrain <- trainingCleaned[inTrain, ]
DataTest <- trainingCleaned[-inTrain, ]
```

## Building our model :
Our model based on 6 folds cross validation to apply the decision tree algorithm to predict classe with all others variables.  

```{r  echo=TRUE}
control <- trainControl(method="cv", 6)
modelFit <- train(classe ~ ., data=DataTrain, method="rpart", trControl=control)
modelFit$finalModel
```

We test our model on test data :  

```{r  echo=TRUE}
predictions <- predict(modelFit, DataTest)
DataTest$classe <- as.factor(DataTest$classe)
confusionMatrix(DataTest$classe,predictions)
```



## Accuracy/ Out of sample error :  

```{r  echo=TRUE}
accuracy <- postResample(predictions, DataTest$classe)
OutSimplError <- 1 - as.numeric(confusionMatrix(DataTest$classe, predictions)$overall[1])
```

The accuracy of our model is 49.67% and the estimated out-of-sample error is 0.50%.  

## Prediction test :  

we apply our prediction to initial data set :     
```{r  echo=TRUE}
pred <- predict(modelFit, testingCleaned[, -53])
pred
```


## Plots :

+ Tree decision :  
```{r  echo=FALSE}
prp(modelFit$finalModel)
```

+ Plot of Total accel belt by each classe :  
  

```{r  echo=FALSE}
qplot(total_accel_belt,colour=classe,data = training,geom="density")
```

